An efficient acyclic contact planner for multiped robots

### 2016-09-05 body/abstract.tex
Nouvel abstract Main.tex change pour pb de compilation.

We present a framework capable of producing contact plans describing complex multiped motions (including humanoid): standing up, climbing stairs using a handrail, crossing rubble and getting out of a car. Our framework answers a need demonstrated at the Darpa Robotics Challenge,
where the lack of an automatic acyclic contact planner was recognized a major issue.

Our novel key idea is the reachability condition. Informally, it verifies that the root configuration of a robot is ``close, but not too close'' from obstacles: close to allow contact creation, not too close to avoid collision. With this approximation of the space of admissible root configurations we decompose the hard contact planning problem into simpler sub-problems: first, to plan a guide path for the root without considering the whole-body configuration; then, to generate a discrete sequence of whole-body configurations in static equilibrium along this path. The reachability condition turns the high-dimensional computation of the guide into a collision checking problem, solved in less than a few seconds. Then a deterministic contact selection algorithm tackles the combinatorial issue of  generating of a discrete sequence along the guide path. Several innovations make it computationally efficient: a criterion for verifying static equilibrium, and a set of heuristics used to enforce desirable properties on the configuration.

>>>>

We describe  a method to plan contacts allowing any multiped robot, including a humanoid, to achieve complex motions: standing up, climbing stairs using a handrail, crossing rubble and getting out of a car.

The Darpa Robotics Challenge recognized the lack  of an automatic acyclic contact planner to be a major issue. We adress by introducing the reachability condition which, informally, verifies that a robot root remains in a bounded volume above the environment surfaces, close enough to allow contact creation and far enough to allow collision free motion of the limbs.  We achieve a complex motion by decomposing the hard contact planning into simpler sub-problems: first, to plan a guide path for the root without considering the whole-body configuration; second, to generate a discrete sequence of whole-body configurations in static equilibrium along this path. The reachability condition turns the high-dimensional computation of the guide into a collision checking problem. Then a deterministic contact selection algorithm tackles the combinatorial issue of  generating of a discrete sequence along the guide path. Several innovations make it computationally efficient: a criterion for verifying static equilibrium, and a set of heuristics used to enforce desirable properties on the configuration.
